### 2016-12-07 paper/chapters/gan.tex
added image for gan architecture (stolen)
additions to GAN stability/performance

@@

\subsection{Stability and Performance}
\label{sub:gan_stability}

\subsubsection{Freeze Learning}
\label{ssub:gan_freeze_learning}

@@

\subsubsection{Label Smoothing}
\label{ssub:gan_label_smoothing}

>>>>

% http://www.slideshare.net/xavigiro/deep-learning-for-computer-vision-generative-models-and-adversarial-training-upc-2016
% TODO: recreate in tikz
\begin{figure}[htb]
\centering
  \includegraphics[width=\linewidth]{media/deep-learning-for-computer-vision-generative-models-and-adversarial-training-upc-2016-5-638.jpg}
  \caption{Conceptual idea of generative adversarial networks (source: Summer seminar UPC TelecomBCN)}\label{fig:gan_architecture}
\end{figure}

@@

\subsection{Stability and Performance}
\label{sub:gan_stability}
In the practical case where both function approximators $G$ and $D$ are represented using a neural network,
GANs have been shown to be difficult to train using gradient descent.
These issues have been credited to the problem of finding the nash equilibrium in the minimax-game with continious, high-dimensional parameters whereas current gradient-based methods are [designed] to reach an minimum.
Additionally to these hypothetical thoughts, \cite{gan_distinguish_crit:2014} have shown that these methods may fail to converge.
Acknoledging these problems, Salimans et al \cite{improved_gan:2016} has studied the stability and performance of GAN in detail resulting in a number of practical methods improving sample generation and improved semi-supervised learning performance.
We will take a look at a selection of these methods in the following, focussing on neural networks as approximators.

\subsubsection{Freeze Learning}
\label{ssub:gan_freeze_learning}
One of the main issues prominent during early GAN research is the disparity between $G$ and $D$.
Commonly during training one of these networks will outpace the other resulting in degraded gradients where the other player is unable to learn from.
Freeze learning is one of the natural counter to this problem, just freezing either $G$ or $D$ until the other network has catched up (formulation!).
In practice the generator is far slower to train than the discriminator in most cases (citation).

\subsubsection{Label Smoothing}
\label{ssub:gan_label_smoothing}
Another basic idea to improve gradient flow is to replace the binary classification values $0/1$ with smoothed values $0.1/0.9$ or $\epsilon/1-\epsilon$.
This guarantees to provide the generator with an informative gradient to improve learning performance
Additionally, smoothed labels have been shown to reduce the attack surface of neural networks to adversarial examples \cite{adv_examples:2016}.
% TODO replace 0/1 with e/1 − e ??
% TODO one-sided label smoothing

@@
